Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2016-03-31 Paper/paper.tex
good quality lambda measurement bias figures

\includegraphics[width=.68\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR20_CI90_0.pdf}
\includegraphics[width=.68\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR30_CI90_0.pdf}
\includegraphics[width=.68\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR50_CI90_0.pdf}\\

@@

\includegraphics[trim={0 0 0 0},width=\columnwidth]{plots/TT_q2-00_mNS1-35_chiBH0-75_Lambda1500-0_SNR20-0_corner_eta_Mc_chi2_Lambda.pdf}
\includegraphics[trim={0 0 0 0},width=\columnwidth]{plots/TT_q2-00_mNS1-35_chiBH0-75_Lambda1500-0_SNR20-0_corner_m1_m2_chi2_Lambda.pdf}
\caption{These figure shows the $1-$ and $2-$dimensional 
\textit{a posteriori} probability distributions 
for different physical parameters describing a BHNS system including NS matter 
effects, as measured by a Bayesian Markov-chain Monte Carlo using tidal templates.
The true parameters of the injected signal are: 
$\mathcal{M}=1.6406M_\odot, \eta=0.2222, \chibh=\chi_2=0.75$ and $\lambdans=1500$,
with the injected SNR $\rho=20$. We show this case as typical of those with the largest
tidal signatures imprinted on the emitted GWs (due to the system being comparable
mass-ratio with a large-aligned spin on the BH and a fairly deformable NS), yet 
with low SNR.
We note a few things:
(i) chirp mass is well constrained, with a nearly-Gaussian probability distribution;
while (ii) the other $3$ less constrained parameters rail against
prior boundaries. The specific boudary conditions that we run into are (a) for $\eta$,
we are limited by the requirement that $m_\mathrm{NS}\geq 1.2M_\odot$ 
of our templates; (b) for BH spin, we are limited by the $\chibh\leq+0.75$ requirement
that results from a template model limitation~\cite{Lackey:2013axa}; and (c) for 
$\lambdans$, we
restrict it to $[0, 4000]$ for the same reason as (b). These prior boundaries
limit the exploration of the entire likelihood surfaces. While (a) is astrophysically
justified, given that we have not observed NSs with masses below 
$1.25M_\odot$, (b) and (c) will be removed in future studies as more evolved template
models become available. See, also, Fig.~\ref{fig:TT_logLikeProb_q2_chi75_L1500_SNR20}.
Finally, we note that the left panel corresponds to the actual sampling parameters,
while the right panel to derived ones.
\label{fig:TT_pdf_q2_chi75_L1500_SNR20}
% \includegraphics[width=.66\columnwidth]{plots/TT_q2-00_mNS1-35_chiBH0-75_Lambda1500-0_SNR20-0_corner_eta_Mc_chi2_Lambda.pdf}
\includegraphics[width=\columnwidth]{plots/TT_logLike_vs_m1_m2_eta0-22_Mc1-64_chi0-00_chi0-50_L1000-0_SNR30.pdf}
\includegraphics[width=\columnwidth]{plots/TT_logProb_vs_m1_m2_eta0-22_Mc1-64_chi0-00_chi0-50_L1000-0_SNR30.pdf}
\caption{These figures show the effect of limitation (a) (described in the caption
of Fig.~\ref{fig:TT_pdf_q2_chi75_L1500_SNR20}) on the likelihood surface portion
that is actually accessible to our Bayesian inferencing algorithm. On the left we show the
entire likelihood surface in the $\mbh-\mns$ plane, while on the left is the 
portion not forbidden by the requirement $\mns\geq 1.2M_\odot$. Similarly, our
priors on BH spin and NS deformability further curtail the portion of sampled
parameter space, albeit to much less impact than this mass cut.}
\label{fig:TT_logLikeProb_q2_chi75_L1500_SNR20}

>>>>

% \includegraphics[width=\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR20_CI90_0.pdf}
\includegraphics[width=1.\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR30_CI90_0.pdf}
\includegraphics[width=1.\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR50_CI90_0.pdf}\\

@@

% \begin{figure*}
% \centering    
% \includegraphics[trim={0 0 0 0},width=\columnwidth]{plots/TT_q2-00_mNS1-35_chiBH0-75_Lambda1500-0_SNR20-0_corner_eta_Mc_chi2_Lambda.pdf}
% \includegraphics[trim={0 0 0 0},width=\columnwidth]{plots/TT_q2-00_mNS1-35_chiBH0-75_Lambda1500-0_SNR20-0_corner_m1_m2_chi2_Lambda.pdf}
% \caption{These figure shows the $1-$ and $2-$dimensional 
% \textit{a posteriori} probability distributions 
% for different physical parameters describing a BHNS system including NS matter 
% effects, as measured by a Bayesian Markov-chain Monte Carlo using tidal templates.
% The true parameters of the injected signal are: 
% $\mathcal{M}=1.6406M_\odot, \eta=0.2222, \chibh=\chi_2=0.75$ and $\lambdans=1500$,
% with the injected SNR $\rho=20$. We show this case as typical of those with the largest
% tidal signatures imprinted on the emitted GWs (due to the system being comparable
% mass-ratio with a large-aligned spin on the BH and a fairly deformable NS), yet 
% with low SNR.
% % 
% We note a few things:
% (i) chirp mass is well constrained, with a nearly-Gaussian probability distribution;
% while (ii) the other $3$ less constrained parameters rail against
% prior boundaries. The specific boudary conditions that we run into are (a) for $\eta$,
% we are limited by the requirement that $m_\mathrm{NS}\geq 1.2M_\odot$ 
% of our templates; (b) for BH spin, we are limited by the $\chibh\leq+0.75$ requirement
% that results from a template model limitation~\cite{Lackey:2013axa}; and (c) for 
% $\lambdans$, we
% restrict it to $[0, 4000]$ for the same reason as (b). These prior boundaries
% limit the exploration of the entire likelihood surfaces. While (a) is astrophysically
% justified, given that we have not observed NSs with masses below 
% $1.25M_\odot$, (b) and (c) will be removed in future studies as more evolved template
% models become available. See, also, Fig.~\ref{fig:TT_logLikeProb_q2_chi75_L1500_SNR20}.
% % 
% Finally, we note that the left panel corresponds to the actual sampling parameters,
% while the right panel to derived ones.
% }
% \label{fig:TT_pdf_q2_chi75_L1500_SNR20}
% \end{figure*}
% %
% \begin{figure*}
% \centering    
% % \includegraphics[width=.66\columnwidth]{plots/TT_q2-00_mNS1-35_chiBH0-75_Lambda1500-0_SNR20-0_corner_eta_Mc_chi2_Lambda.pdf}
% \includegraphics[width=\columnwidth]{plots/TT_logLike_vs_m1_m2_eta0-22_Mc1-64_chi0-00_chi0-50_L1000-0_SNR30.pdf}
% \includegraphics[width=\columnwidth]{plots/TT_logProb_vs_m1_m2_eta0-22_Mc1-64_chi0-00_chi0-50_L1000-0_SNR30.pdf}
% \caption{These figures show the effect of limitation (a) (described in the caption
% of Fig.~\ref{fig:TT_pdf_q2_chi75_L1500_SNR20}) on the likelihood surface portion
% that is actually accessible to our Bayesian inferencing algorithm. On the left we show the
% entire likelihood surface in the $\mbh-\mns$ plane, while on the left is the 
% portion not forbidden by the requirement $\mns\geq 1.2M_\odot$. Similarly, our
% priors on BH spin and NS deformability further curtail the portion of sampled
% parameter space, albeit to much less impact than this mass cut.}
% \label{fig:TT_logLikeProb_q2_chi75_L1500_SNR20}
% \end{figure*}
